Synthesizing Optimal Sizing of Stand-alone Solar Photovoltaic Systems\\

### 2019-05-03 Tex/ASE2019/Conference-LaTeX-template_7-9-18/paperv0.tex
reviewed abstract
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\begin{abstract}
Currently, there exist various state-of-the-art tools to design PV systems, but they are mainly based on simulations, which do not cover all aspects of the design-space. We present a sound and automated approach to synthesize optimal sizing of stand-alone solar photovoltaic (PV) systems. The application of program synthesis to design PV systems is a very recent subject that has not been further explored. Here we develop and evaluate an automated formal synthesis approach based on program synthesis and report preliminary results to optimize the sizing of a PV system. Commercial equipment data is provided to our synthesis engine and a candidate solution is derived from financial analysis of the obtained sizing. Our proposed synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results show that our synthesis method, based on symbolic model checking as our main verification engine, is able to synthesize within an acceptable run-time the optimal PV system sizing of two different case studies.
\end{abstract}

>>>>

\begin{abstract}
Currently, there exist various state-of-the-art tools to design solar photovoltaic (PV) systems, but they are mainly based on simulations, which do not cover all aspects of the design-space. We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis. 
In particular, our counterexample guided inductive synthesis (CEGIS) approach has two phases: we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost. The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained. Commercial equipment data is provided to our synthesis engine and candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of two different intricate case studies.
\end{abstract}
